---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.retina = 2,
  dpi = 300,
  out.width = "100%"
)
```

# simulariatools

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.165117.svg)](https://doi.org/10.5281/zenodo.596741)

`simulariatools` is a collection of functions and tools useful to pre and post
process data for air quality assessment. 
The package is developed and maintained by the people at [Simularia](https://www.simularia.it)
and it is extensively used therein for daily jobs.

If you use this package in your work, please consider citing it.
Refer to its [Zenodo DOI](https://doi.org/10.5281/zenodo.596741) to cite it.


## Installation

Installation of `simulariatools` from GitHub can be easily done using the `devtools` package:

```{r eval=FALSE, include=TRUE}
    library("devtools")
    install_github("Simularia/simulariatools")
```

The same commands can also be used to upgrade the package.

We also try to keep up to date versions of the package 
[here](https://www.dropbox.com/sh/71252ydg6h3xvgc/AADiWKkh_tJHK97e5-ILAQVWa?dl=0) 
if you can’t build the package yourself.

Note: in order to use `importADSOBIN()` to import *ADSO/BIN* data files, 
a working installation of *Python 3* is required.

## Brief examples

### Contour plot

Air quality data from *NetCDF* or *ADSO/BIN* files need to be imported first.
```{r eval=TRUE, include=TRUE}
library(simulariatools)
mydata <- importRaster(file = "./test/ave_anno_nox_all.nc",
                       k = 1000,
                       destaggering = TRUE,
                       variable = "NOX",
                       verbose = TRUE)
```

By running *contourPlot2()* without any argument, a quick plot with default customization
is obtained:
```{r}
contourPlot2(mydata)
```
The plot is easily customizable by using *contourPlot2()* arguments and by piping *ggplot2* instructions:
```{r}
library(ggplot2)
contourPlot2(mydata, 
             domain = c(280000, 303000, 5028000, 5052000, 5, 5),
             levels = c(-Inf, 10, 15, 20, 30, 40),
             legend = "NOx [ug/m3]") + 
  labs(x = NULL, y = NULL) +
  theme_minimal()
```



## List of functions

- `contpourPlot2()`
- `downloadBasemap()`
- `importRaster()`.
- `importADSOBIN()`.
- `importSurferGrd()`.
- `plotAvgRad()`.
- `plotAvgTemp()`.
- `plotStabilityClass()`.
- `removeOutliers()`.
- `rollingMax()`.
- `stabilityClass()`.
- `vectorField()`.
- `contourPlot()` obsolete.
- `createBaseMap()` obsolete.


If you are interested, you can track development and contribute at http://github.com/simularia/simulariatools

## Contact

Contact person:
    Giuseppe Carlino
    Simularia s.r.l.
    g.carlino@simularia.it


## Contributors

Matteo Paolo Costa


## License

`simulariatools` is distributed under the GPL-2 license.
