---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simulariatools

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.165117.svg)](https://doi.org/10.5281/zenodo.596741)
<!-- badges: end -->

`simulariatools` is a collection of functions and tools useful to pre and post
process data for air quality assessment. It is developed and maintained by the
people at [Simularia](www.simularia.it).

If you use this package in your work, please consider citing it.
Refer to its [Zenodo DOI to cite it](https://doi.org/10.5281/zenodo.596741).


## Installation

Installation of `simulariatools` from GitHub can be easily using the `devtools` package:

```{r eval=FALSE, include=TRUE}
    library("devtools")
    install_github("Simularia/simulariatools")
```

The same commands can also be used to upgrade the package.

We also try to keep up to date versions of the package 
[here](https://www.dropbox.com/sh/71252ydg6h3xvgc/AADiWKkh_tJHK97e5-ILAQVWa?dl=0) 
if you can’t build the package yourself.

## List of functions

- `contpourPlot2()`
- `downloadBasemap()`
- `importRaster()`.
- `importADSOBIN()`.
- `importSurferGrd()`.
- `plotAvgRad()`.
- `plotAvgTemp()`.
- `plotStabilityClass()`.
- `removeOutliers()`.
- `rollingMax()`.
- `stabilityClass()`.
- `vectorField()`.
- `contourPlot()` obsolete.
- `createBaseMap()` obsolete.


If you are interested, you can track development and contribute at http://github.com/simularia/simulariatools

Contact person:
    Giuseppe Carlino
    Simularia s.r.l.
    g.carlino@simularia.it


## Contributors

Matteo Paolo Costa


## License

`simulariatools` is distributed under the GPL-2 license.
